data_proprocessing

### 2021-03-22 code/data_load.Rmd

```{r All info files}
# Messueberblick
Messueberblick_path <- "/data/p_02161/ADI_studie/metadata/ADI_MRT_Messueberblick_2019_04_10.csv"

# ADI_Aktuell  -  main table, BMI info is refilled with Messueberblick entries
ADIAktuell_path <- "/data/p_02161/ADI_studie/metadata/Daten ADI aktuell.sav"

# QOL_sheet  -  correct group information (unused, just for comparison)
QOLsheet_path <- "/data/pt_02161/Results/Project1_headmotion/QOL_sheet_of_ADI_Messueberblick.csv"

# summary_with_SPSS  - table has errors (contradictions for ADI080 and ADI036 with other table, but contains missing subjects)
GroupCodingWitErrors_path <- "/data/pt_02161/Results/Project1_headmotion/summary_with_SPSS_data_sheet_of_ADI_Messueberblick.csv"

# rs QA infos
rsQA_path <- "/data/pt_02161/Analysis/Preprocessing/qa/rs_qa/ADI_rs_qa.csv"

# FS infos
FSqa_path <- "/data/p_02161/ADI_studie/BIDS/derivatives/freesurfer/QA/freesurfer_qa_qoala_11.7.csv"

# subjects_rs  -  Loading mean/max FD values
rsID_path <- "/data/pt_02161/Results/Project1_headmotion/subjects_rs.csv"
FDvals_path <- "/data/pt_02161/Results/Project1_headmotion/summary_FDvals_correctADI061.csv"

# output
out_path <- "/data/p_02161/ADI_studie/metadata/final_sample_MRI_QA_info.csv"
```
### Loading Demographics
We get BMI from `ADI_MRT_Messueberblick_2019_04.csv` (this is an older version with correct columns (compared to _AW.xlsx). See README in `/data/p_02161/ADI_studie/metadata/`.

@@

```{r "Load data", include=FALSE}
# read "Messüberblick"
# collect subject IDs in one column "BMI"
bmi = read.csv(
  "/data/p_02161/ADI_studie/metadata/ADI_MRT_Messueberblick_2019_04_10.csv",
  na.strings = c("", "NA"),
  stringsAsFactors = FALSE
)[, c("X.1",
      "BMI",
      "X.2",
      "BMI.1",
      "X.3",
      "BMI.2",
      "Geschlecht",
      "Alter")]

@@

# get BMI data from another ADI table which contains more subjects
# select variables: only BMI
bmi_repl = haven::read_sav("/data/p_02161/ADI_studie/metadata/Daten ADI aktuell.sav")[, c(
  "ADI_Code",
  "BMI_BL",
  "BMI_6m",
  "BMI_12m",
  "Sex",
  "Age_BL",
  "Age_6m",
  "Age_12m",
  "Educa_BL"
)]
bmi_repl$subj.ID = gsub("-", "", bmi_repl$ADI_Code)

@@

```{r "Compare merged_bmi with bmi from QOL list", include=FALSE }
# does not use QOL list further on
# compare merged_bmi (ADI_aktuell.sav/ Messueberblick) with bmi from QOL list for those subjects who have it
QOL_sheet = read.csv(
  "/data/pt_02161/Results/Project1_headmotion/QOL_sheet_of_ADI_Messueberblick.csv"
)
QOL_sheet$subj.ID = gsub("-", "", QOL_sheet$X.1)

@@

# this table has errors (contradictions for ADI080 and ADI036 with other table, but contains missing subjects)
group_coding_with_errors = read.csv(
  "/data/pt_02161/Results/Project1_headmotion/summary_with_SPSS_data_sheet_of_ADI_Messueberblick.csv"
)
group_coding_with_errors$subj.ID = gsub("-", "", group_coding_with_errors$Copy.SPSS)

@@

```{r "Loading rs QA infos from /data/pt_02161/Analysis/Preprocessing/qa/rs_qa/ADI_rs_qa.csv", echo=FALSE}
rs_QA=read.csv("/data/pt_02161/Analysis/Preprocessing/qa/rs_qa/ADI_rs_qa.csv")
for (i in 1:nrow(rs_QA)){
  #print(strsplit(toString(rs_QA[i,1]),'_')[[1]][1])
  rs_QA[i,"subj.ID"]=strsplit(toString(rs_QA[i,1]),'_')[[1]][1]
  rs_QA[i,"tp"]=strsplit(toString(rs_QA[i,1]),'_')[[1]][2]
}

@@

See `/data/pt_02161/Analysis/Preprocessing/qa/README.md` for further information.
```{r "Loading FS infos from /data/p_02161/ADI_studie/BIDS/derivatives/freesurfer/QA/freesurfer_qa_qoala_11.7.csv", echo=FALSE}
FS_QA=read.csv("/data/p_02161/ADI_studie/BIDS/derivatives/freesurfer/QA/freesurfer_qa_qoala_11.7.csv")
for (i in 1:nrow(FS_QA)){
  #print(strsplit(toString(rs_QA[i,1]),'_')[[1]][1])
  FS_QA[i,"subj.ID"]=strsplit(toString(FS_QA[i,1]),'_')[[1]][1]
  FS_QA[i,"tp"]=strsplit(toString(FS_QA[i,1]),'_')[[1]][2]
}

@@

These values describe the average and maximal motion during rsfMRI scans. Used for manuscript on head motion. See further information in `/data/pt_02161/Analysis/Project1_headmotion/`.
```{r "Loading mean/max FD values from /data/pt_02161/Analysis/Preprocessing/qa/rs_qa/ADI_rs_qa.csv", echo=FALSE}
rs_ID = read.csv("/data/pt_02161/Results/Project1_headmotion/subjects_rs.csv")
colnames(rs_ID)[1] = "subj"
res = read.csv(
  "/data/pt_02161/Results/Project1_headmotion/summary_FDvals_correctADI061.csv",
  header = FALSE
)
colnames(res) = c("meanFD_bl",
                  "maxFD_bl",
                  "meanFD_fu",
                  "maxFD_fu",
                  "meanFD_fu2",
                  "maxFD_fu2")
rs_FD = data.frame(rs_ID$subj, res)
colnames(rs_FD)[1] = "subj.ID"
rs_FD[rs_FD == 0] = NA

@@

```{r, include=FALSE}
write.csv(final_sample, "/data/p_02161/ADI_studie/metadata/final_sample_MRI_QA_info.csv")
```

>>>>

```{r All info files}
# Messueberblick
Messueberblick_path <- "/data/p_02161/ADI_studie/metadata/ADI_MRT_Messueberblick_2019_04_10.csv"
# ADI_Aktuell  -  main table, BMI info is refilled with Messueberblick entries
ADIAktuell_path <- "/data/p_02161/ADI_studie/metadata/Daten ADI aktuell.sav"
# QOL_sheet  -  correct group information (unused, just for comparison)
QOLsheet_path <- "/data/pt_02161/Results/Project1_headmotion/QOL_sheet_of_ADI_Messueberblick.csv"
# summary_with_SPSS  - table has errors (contradictions for ADI080 and ADI036 with other table, but contains missing subjects group allocation)
GroupCodingWitErrors_path <- "/data/pt_02161/Results/Project1_headmotion/summary_with_SPSS_data_sheet_of_ADI_Messueberblick.csv"
# rs QA infos
rsQA_path <- "/data/pt_02161/Analysis/Preprocessing/qa/rs_qa/ADI_rs_qa.csv"
# Freesurfer infos
FSqa_path <- "/data/p_02161/ADI_studie/BIDS/derivatives/freesurfer/QA/freesurfer_qa_qoala_11.7.csv"
# subjects_rs  -  Loading mean/max FD values
rsID_path <- "/data/pt_02161/Results/Project1_headmotion/subjects_rs.csv"
FDvals_path <- FDvals_path
# output
out_path <- "/data/p_02161/ADI_studie/metadata/final_sample_MRI_QA_info.csv"
```
### Loading Demographics
We get BMI from `ADI_MRT_Messueberblick_2019_04.csv` (this is an older version with correct columns (compared to _AW.xlsx). See README in `/data/p_02161/ADI_studie/metadata/`.

@@

```{r "Load data", include=FALSE}
# read "Messüberblick"
# collect subject IDs in one column "BMI"
bmi = read.csv(
  Messueberblick_path,
  na.strings = c("", "NA"),
  stringsAsFactors = FALSE
)[, c("X.1",
      "BMI",
      "X.2",
      "BMI.1",
      "X.3",
      "BMI.2",
      "Geschlecht",
      "Alter")]

@@

# get BMI data from another ADI table which contains more subjects
# select variables: only BMI
bmi_repl = haven::read_sav(ADIAktuell_üath)[, c(
  "ADI_Code",
  "BMI_BL",
  "BMI_6m",
  "BMI_12m",
  "Sex",
  "Age_BL",
  "Age_6m",
  "Age_12m",
  "Educa_BL"
)]
bmi_repl$subj.ID = gsub("-", "", bmi_repl$ADI_Code)

@@

```{r "Compare merged_bmi with bmi from QOL list", include=FALSE }
# does not use QOL list further on
# compare merged_bmi (ADI_aktuell.sav/ Messueberblick) with bmi from QOL list for those subjects who have it
QOL_sheet = read.csv(
  QOLsheet_path
)
QOL_sheet$subj.ID = gsub("-", "", QOL_sheet$X.1)

@@

# this table has errors (contradictions for ADI080 and ADI036 with other table, but contains missing subjects)
group_coding_with_errors = read.csv(
  GroupCodingWitErrors_path
)
group_coding_with_errors$subj.ID = gsub("-", "", group_coding_with_errors$Copy.SPSS)

@@

```{r "Loading rs QA infos from /data/pt_02161/Analysis/Preprocessing/qa/rs_qa/ADI_rs_qa.csv", echo=FALSE}
rs_QA=read.csv(rsQA_path)
for (i in 1:nrow(rs_QA)){
  #print(strsplit(toString(rs_QA[i,1]),'_')[[1]][1])
  rs_QA[i,"subj.ID"]=strsplit(toString(rs_QA[i,1]),'_')[[1]][1]
  rs_QA[i,"tp"]=strsplit(toString(rs_QA[i,1]),'_')[[1]][2]
}

@@

See `/data/pt_02161/Analysis/Preprocessing/qa/README.md` for further information.
```{r "Loading FS infos from /data/p_02161/ADI_studie/BIDS/derivatives/freesurfer/QA/freesurfer_qa_qoala_11.7.csv", echo=FALSE}
FS_QA=read.csv(FSqa_path)
for (i in 1:nrow(FS_QA)){
  #print(strsplit(toString(rs_QA[i,1]),'_')[[1]][1])
  FS_QA[i,"subj.ID"]=strsplit(toString(FS_QA[i,1]),'_')[[1]][1]
  FS_QA[i,"tp"]=strsplit(toString(FS_QA[i,1]),'_')[[1]][2]
}

@@

These values describe the average and maximal motion during rsfMRI scans. Used for manuscript on head motion. See further information in `/data/pt_02161/Analysis/Project1_headmotion/`.
```{r "Loading mean/max FD values from /data/pt_02161/Analysis/Preprocessing/qa/rs_qa/ADI_rs_qa.csv", echo=FALSE}
rs_ID = read.csv(rsID_path)
colnames(rs_ID)[1] = "subj"
res = read.csv(
  FDvals_path,
  header = FALSE
)
colnames(res) = c("meanFD_bl",
                  "maxFD_bl",
                  "meanFD_fu",
                  "maxFD_fu",
                  "meanFD_fu2",
                  "maxFD_fu2")
rs_FD = data.frame(rs_ID$subj, res)
colnames(rs_FD)[1] = "subj.ID"
rs_FD[rs_FD == 0] = NA

@@

```{r, include=FALSE}
write.csv(final_sample, out_path)
```
